---
title: "ccd35PastPrimaries"
author: "YingtongZhou"
date: "01/04/2021"
output: html_document
---

```{r setup, include=FALSE}
setwd("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies")
```

Load Packages
```{r}
library(dplyr)
library(stringr)
library(readxl)
```


# Load ccd35 & 2017 ccd primaries
```{r}
ccd35 <- read.delim("ccd35.txt", stringsAsFactors = FALSE)
ccd35$ed <- paste(formatC(as.integer(sub("/.*", "", ccd35$ed)), width=3, flag="0"),
                 str_sub(ccd35$ed, -2,-1), sep = "/")

cc17p <- read.csv("ccd35_17dp.csv", header = TRUE, stringsAsFactors = FALSE)
cc17p$ed <- paste(formatC(cc17p$ED, width=3, flag="0"), formatC(cc17p$AD, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
cc17p_ab <- cc17p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Absentee / Military") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
write.csv(cc17p_ab, "cc17p_ab.csv")
```


Ede S. Fox
```{r}
cc17p_fox <- cc17p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Ede S. Fox") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
write.csv(cc17p_fox, "cc17p_fox.csv")
```


Laurie A. Cumbo
```{r}
cc17p_cumbo <- cc17p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Laurie A. Cumbo") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
write.csv(cc17p_cumbo, "cc17p_cumbo.csv")
```


# Load ad43_20p
```{r}
ad43_20p <- read.csv("ad43_20p.csv", header = FALSE, stringsAsFactors = FALSE)
ad43_20p$ed <- paste(formatC(ad43_20p$V2, width=3, flag="0"), formatC(ad43_20p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ad43_20p_re <- ad43_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Absentee / Military") %>% 
  select(-V3) %>% 
  right_join(ccd35, by = "ed")
names(ad43_20p_re)[names(ad43_20p_re) == "V4"] <- "ab"
```


Jesse E. Hamilton
```{r}
ad43_20p_re <- ad43_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Jesse E. Hamilton") %>% 
  select(-V3) %>% 
  right_join(ad43_20p_re, by = "ed")
names(ad43_20p_re)[names(ad43_20p_re) == "V4"] <- "jh"
```


Diana Richardson
```{r}
ad43_20p_re <- ad43_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Diana Richardson") %>% 
  select(-V3) %>% 
  right_join(ad43_20p_re, by = "ed")
names(ad43_20p_re)[names(ad43_20p_re) == "V4"] <- "dr"

write.csv(ad43_20p_re, "ad43_20p_re.csv")
```


# Load ad43_15sp
```{r}
ad43_15sp <- read.csv("ad43_15sp.csv", header = TRUE, stringsAsFactors = FALSE)
ad43_15sp$ed <- paste(formatC(ad43_15sp$ED, width=3, flag="0"), formatC(ad43_15sp$AD, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ad43_15sp_re <- ad43_15sp %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Absentee/Military") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
names(ad43_15sp_re)[names(ad43_15sp_re) == "Tally"] <- "ab"
```


Menachem M. Raitport
```{r}
ad43_15sp_re <- ad43_15sp %>% 
  select(-AD, -ED) %>% 
  filter(grepl('Menachem M. Raitport', Unit.Name)) %>% 
  select(-Unit.Name) %>% 
  group_by(ed) %>% 
  summarise(mr= sum(Tally)) %>% 
  right_join(ad43_15sp_re, by = "ed")
names(ad43_15sp_re)[names(ad43_15sp_re) == "Tally"] <- "mr"
```


Diana Richardson
```{r}
ad43_15sp_re <- ad43_15sp %>% 
  select(-AD, -ED) %>% 
  filter(grepl('Diana C. Richardson', Unit.Name)) %>% 
  select(-Unit.Name) %>% 
  right_join(ad43_15sp_re, by = "ed")
names(ad43_15sp_re)[names(ad43_15sp_re) == "Tally"] <- "dr"
```


Shirley M. Patterson
```{r}
ad43_15sp_re <- ad43_15sp %>% 
  select(-AD, -ED) %>% 
  filter(grepl('Shirley M. Patterson', Unit.Name)) %>% 
  select(-Unit.Name) %>% 
  right_join(ad43_15sp_re, by = "ed")
names(ad43_15sp_re)[names(ad43_15sp_re) == "Tally"] <- "sp"
```


Geoffrey A. Davis
```{r}
ad43_15sp_re <- ad43_15sp %>% 
  select(-AD, -ED) %>% 
  filter(grepl('Geoffrey A. Davis', Unit.Name)) %>% 
  select(-Unit.Name) %>% 
  right_join(ad43_15sp_re, by = "ed")
names(ad43_15sp_re)[names(ad43_15sp_re) == "Tally"] <- "gd"

write.csv(ad43_15sp_re, "ad43_15sp_re.csv")
```


# Load ad50_20p
```{r}
ad50_20p <- read.csv("ad50_20p.csv", header = FALSE, stringsAsFactors = FALSE)
ad50_20p$ed <- paste(formatC(ad50_20p$V2, width=3, flag="0"), formatC(ad50_20p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ad50_20p_re <- ad50_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Absentee / Military") %>% 
  select(-V3) %>% 
  right_join(ccd35, by = "ed")
names(ad50_20p_re)[names(ad50_20p_re) == "V4"] <- "ab"
```


Emily E. Gallagher
```{r}
ad50_20p_re <- ad50_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Emily E. Gallagher") %>% 
  select(-V3) %>% 
  right_join(ad50_20p_re, by = "ed")
names(ad50_20p_re)[names(ad50_20p_re) == "V4"] <- "eg"
```


Joseph R. Lentol
```{r}
ad50_20p_re <- ad50_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Joseph R. Lentol") %>% 
  select(-V3) %>% 
  right_join(ad50_20p_re, by = "ed")
names(ad50_20p_re)[names(ad50_20p_re) == "V4"] <- "jl"

write.csv(ad50_20p_re, "ad50_20p_re.csv")
```


# Load ad52_14p
```{r}
ad52_14p <- read.csv("ad52_14p.csv", header = TRUE, stringsAsFactors = FALSE)
ad52_14p$ed <- paste(formatC(ad52_14p$ED, width=3, flag="0"), formatC(ad52_14p$AD, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ad52_14p_re <- ad52_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Absentee/Military") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
names(ad52_14p_re)[names(ad52_14p_re) == "Tally"] <- "ab"
```


Jo Anne Simon
```{r}
ad52_14p_re <- ad52_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Jo Anne Simon") %>% 
  select(-Unit.Name) %>% 
  right_join(ad52_14p_re, by = "ed")
names(ad52_14p_re)[names(ad52_14p_re) == "Tally"] <- "js"
```


Peter J. Sikora
```{r}
ad52_14p_re <- ad52_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Peter J. Sikora") %>% 
  select(-Unit.Name) %>% 
  right_join(ad52_14p_re, by = "ed")
names(ad52_14p_re)[names(ad52_14p_re) == "Tally"] <- "ps"
```


Doug Biviano
```{r}
ad52_14p_re <- ad52_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Doug Biviano") %>% 
  select(-Unit.Name) %>% 
  right_join(ad52_14p_re, by = "ed")
names(ad52_14p_re)[names(ad52_14p_re) == "Tally"] <- "db"

write.csv(ad52_14p_re, "ad52_14p_re.csv")
```


# Load ad56_20p
```{r}
ad56_20p <- read.csv("ad56_20p.csv", header = FALSE, stringsAsFactors = FALSE)
ad56_20p$ed <- paste(formatC(ad56_20p$V2, width=3, flag="0"), formatC(ad56_20p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ad56_20p_re <- ad56_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Absentee / Military") %>% 
  select(-V3) %>% 
  right_join(ccd35, by = "ed")
names(ad56_20p_re)[names(ad56_20p_re) == "V4"] <- "ab"
```


Justin Cohen
```{r}
ad56_20p_re <- ad56_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Justin Cohen") %>% 
  select(-V3) %>% 
  right_join(ad56_20p_re, by = "ed")
names(ad56_20p_re)[names(ad56_20p_re) == "V4"] <- "jc"
```


Stefani L. Zinerman
```{r}
ad56_20p_re <- ad56_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Stefani L. Zinerman") %>% 
  select(-V3) %>% 
  right_join(ad56_20p_re, by = "ed")
names(ad56_20p_re)[names(ad56_20p_re) == "V4"] <- "sz"

write.csv(ad56_20p_re, "ad56_20p_re.csv")
```


# Load ad56_16p
```{r}
ad56_16p <- read.csv("ad56_16p.csv", header = TRUE, stringsAsFactors = FALSE)
ad56_16p$ed <- paste(formatC(ad56_16p$ED, width=3, flag="0"), formatC(ad56_16p$AD, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ad56_16p_re <- ad56_16p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Absentee/Military") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
names(ad56_16p_re)[names(ad56_16p_re) == "Tally"] <- "ab"
```


Karen Z. Cherry
```{r}
ad56_16p_re <- ad56_16p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Karen Z. Cherry") %>% 
  select(-Unit.Name) %>% 
  right_join(ad56_16p_re, by = "ed")
names(ad56_16p_re)[names(ad56_16p_re) == "Tally"] <- "kc"
```


Tremaine S. Wright
```{r}
ad56_16p_re <- ad56_16p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Tremaine S. Wright") %>% 
  select(-Unit.Name) %>% 
  right_join(ad56_16p_re, by = "ed")
names(ad56_16p_re)[names(ad56_16p_re) == "Tally"] <- "tw"

write.csv(ad56_16p_re, "ad56_16p_re.csv")
```


# Load ad57_20p
```{r}
ad57_20p <- read.csv("ad57_20p.csv", header = FALSE, stringsAsFactors = FALSE)
ad57_20p$ed <- paste(formatC(ad57_20p$V2, width=3, flag="0"), formatC(ad57_20p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ad57_20p_re <- ad57_20p %>% 
  select(-V1, -V2, -V3) %>% 
  filter(V4 == "Absentee / Military") %>% 
  select(-V4) %>% 
  right_join(ccd35, by = "ed")
names(ad57_20p_re)[names(ad57_20p_re) == "V5"] <- "ab"
```


Walter T. Mosley III
```{r}
ad57_20p_re <- ad57_20p %>% 
  select(-V1, -V2, -V3) %>% 
  filter(V4 == "Walter T. Mosley III") %>% 
  select(-V4) %>% 
  right_join(ad57_20p_re, by = "ed")
names(ad57_20p_re)[names(ad57_20p_re) == "V5"] <- "wm"
```


Phara Souffrant Forrest
```{r}
ad57_20p_re <- ad57_20p %>% 
  select(-V1, -V2, -V3) %>% 
  filter(V4 == "Phara Souffrant Forrest") %>% 
  select(-V4) %>% 
  right_join(ad57_20p_re, by = "ed")
names(ad57_20p_re)[names(ad57_20p_re) == "V5"] <- "pf"

write.csv(ad57_20p_re, "ad57_20p_re.csv")
```


# Load ss20_18p
```{r}
ss20_18p <- read.csv("ss20_18p.csv", header = FALSE, stringsAsFactors = FALSE)
ss20_18p$ed <- paste(formatC(ss20_18p$V2, width=3, flag="0"), formatC(ss20_18p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ss20_18p_re <- ss20_18p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Absentee / Military") %>% 
  select(-V3) %>% 
  right_join(ccd35, by = "ed")
names(ss20_18p_re)[names(ss20_18p_re) == "V4"] <- "ab"
```


Jesse E. Hamilton
```{r}
ss20_18p_re <- ss20_18p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Jesse E. Hamilton") %>% 
  select(-V3) %>% 
  right_join(ss20_18p_re, by = "ed")
names(ss20_18p_re)[names(ss20_18p_re) == "V4"] <- "jh"
```


Zellnor Y. Myrie
```{r}
ss20_18p_re <- ss20_18p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Zellnor Y. Myrie") %>% 
  select(-V3) %>% 
  right_join(ss20_18p_re, by = "ed")
names(ss20_18p_re)[names(ss20_18p_re) == "V4"] <- "zm"

write.csv(ss20_18p_re, "ss20_18p_re.csv")
```


# Load ss20_14p
```{r}
ss20_14p <- read.csv("ss20_14p.csv", header = TRUE, stringsAsFactors = FALSE)
ss20_14p$ed <- paste(formatC(ss20_14p$ED, width=3, flag="0"), formatC(ss20_14p$AD, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ss20_14p_re <- ss20_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Absentee/Military") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
names(ss20_14p_re)[names(ss20_14p_re) == "Tally"] <- "ab"
```


Guillermo E. Philpotts	
```{r}
ss20_14p_re <- ss20_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Guillermo E. Philpotts") %>% 
  select(-Unit.Name) %>% 
  right_join(ss20_14p_re, by = "ed")
names(ss20_14p_re)[names(ss20_14p_re) == "Tally"] <- "gp"
```


Rubain J. Dorancy
```{r}
ss20_14p_re <- ss20_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Rubain J. Dorancy") %>% 
  select(-Unit.Name) %>% 
  right_join(ss20_14p_re, by = "ed")
names(ss20_14p_re)[names(ss20_14p_re) == "Tally"] <- "rd"
```


Jesse E. Hamilton
```{r}
ss20_14p_re <- ss20_14p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Jesse E. Hamilton") %>% 
  select(-Unit.Name) %>% 
  right_join(ss20_14p_re, by = "ed")
names(ss20_14p_re)[names(ss20_14p_re) == "Tally"] <- "jh"

write.csv(ss20_14p_re, "ss20_14p_re.csv")
```


# Load ss25_20p
```{r}
ss25_20p <- read.csv("ss25_20p.csv", header = FALSE, stringsAsFactors = FALSE)
ss25_20p$ed <- paste(formatC(ss25_20p$V2, width=3, flag="0"), formatC(ss25_20p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ss25_20p_re <- ss25_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Absentee / Military") %>% 
  select(-V3) %>% 
  right_join(ccd35, by = "ed")
names(ss25_20p_re)[names(ss25_20p_re) == "V4"] <- "ab"
```


Jabari Brisport
```{r}
ss25_20p_re <- ss25_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Jabari Brisport") %>% 
  select(-V3) %>% 
  right_join(ss25_20p_re, by = "ed")
names(ss25_20p_re)[names(ss25_20p_re) == "V4"] <- "jb"
```


Tremaine S. Wright
```{r}
ss25_20p_re <- ss25_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Tremaine S. Wright") %>% 
  select(-V3) %>% 
  right_join(ss25_20p_re, by = "ed")
names(ss25_20p_re)[names(ss25_20p_re) == "V4"] <- "tw"
```


Jason Salmon
```{r}
ss25_20p_re <- ss25_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Jason Salmon") %>% 
  select(-V3) %>% 
  right_join(ss25_20p_re, by = "ed")
names(ss25_20p_re)[names(ss25_20p_re) == "V4"] <- "js"

write.csv(ss25_20p_re, "ss25_20p_re.csv")
```


# Load ss25_16p
```{r}
ss25_16p <- read.csv("ss25_16p.csv", header = TRUE, stringsAsFactors = FALSE)
ss25_16p$ed <- paste(formatC(ss25_16p$ED, width=3, flag="0"), formatC(ss25_16p$AD, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
ss25_16p_re <- ss25_16p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Absentee/Military") %>% 
  select(-Unit.Name) %>% 
  right_join(ccd35, by = "ed")
names(ss25_16p_re)[names(ss25_16p_re) == "Tally"] <- "ab"
```


Michael G. Cox
```{r}
ss25_16p_re <- ss25_16p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Michael G. Cox") %>% 
  select(-Unit.Name) %>% 
  right_join(ss25_16p_re, by = "ed")
names(ss25_16p_re)[names(ss25_16p_re) == "Tally"] <- "mc"
```


Velmanette Montgomery
```{r}
ss25_16p_re <- ss25_16p %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Velmanette Montgomery") %>% 
  select(-Unit.Name) %>% 
  right_join(ss25_16p_re, by = "ed")
names(ss25_16p_re)[names(ss25_16p_re) == "Tally"] <- "vm"

write.csv(ss25_16p_re, "ss25_16p_re.csv")
```


# Load cd9_20p
```{r}
cd9_20p <- read.csv("cd9_20p.csv", header = FALSE, stringsAsFactors = FALSE)
cd9_20p$ed <- paste(formatC(cd9_20p$V2, width=3, flag="0"), formatC(cd9_20p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
cd9_20p_re <- cd9_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Absentee / Military") %>% 
  select(-V3) %>% 
  right_join(ccd35, by = "ed")
names(cd9_20p_re)[names(cd9_20p_re) == "V4"] <- "ab"
```


Isiah James
```{r}
cd9_20p_re <- cd9_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Isiah James") %>% 
  select(-V3) %>% 
  right_join(cd9_20p_re, by = "ed")
names(cd9_20p_re)[names(cd9_20p_re) == "V4"] <- "ij"
```


Chaim M. Deutsch
```{r}
cd9_20p_re <- cd9_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Chaim M. Deutsch") %>% 
  select(-V3) %>% 
  right_join(cd9_20p_re, by = "ed")
names(cd9_20p_re)[names(cd9_20p_re) == "V4"] <- "cd"
```


Adem Bunkeddeko
```{r}
cd9_20p_re <- cd9_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Adem Bunkeddeko") %>% 
  select(-V3) %>% 
  right_join(cd9_20p_re, by = "ed")
names(cd9_20p_re)[names(cd9_20p_re) == "V4"] <- "adem"
```


Lutchi Gayot
```{r}
cd9_20p_re <- cd9_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Lutchi Gayot") %>% 
  select(-V3) %>% 
  right_join(cd9_20p_re, by = "ed")
names(cd9_20p_re)[names(cd9_20p_re) == "V4"] <- "lg"
```


Yvette D. Clarke
```{r}
cd9_20p_re <- cd9_20p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Yvette D. Clarke") %>% 
  select(-V3) %>% 
  right_join(cd9_20p_re, by = "ed")
names(cd9_20p_re)[names(cd9_20p_re) == "V4"] <- "yc"

write.csv(cd9_20p_re, "cd9_20p_re.csv")
```


# Load cd9_18p
```{r}
cd9_18p <- read.csv("cd9_18p.csv", header = FALSE, stringsAsFactors = FALSE)
cd9_18p$ed <- paste(formatC(cd9_18p$V2, width=3, flag="0"), formatC(cd9_18p$V1, width=2, flag="0"), sep="/")
```


Absentee / Military
```{r}
cd9_18p_re <- cd9_18p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Absentee / Military") %>% 
  select(-V3) %>% 
  right_join(ccd35, by = "ed")
names(cd9_18p_re)[names(cd9_18p_re) == "V4"] <- "ab"
```


Adem Bunkeddeko
```{r}
cd9_18p_re <- cd9_18p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Adem Bunkeddeko") %>% 
  select(-V3) %>% 
  right_join(cd9_18p_re, by = "ed")
names(cd9_18p_re)[names(cd9_18p_re) == "V4"] <- "adem"
```


Yvette D. Clarke
```{r}
cd9_18p_re <- cd9_18p %>% 
  select(-V1, -V2) %>% 
  filter(V3 == "Yvette D. Clarke") %>% 
  select(-V3) %>% 
  right_join(cd9_18p_re, by = "ed")
names(cd9_18p_re)[names(cd9_18p_re) == "V4"] <- "yc"

write.csv(cd9_18p_re, "cd9_18p_re.csv")
```
