---
title: "ED_Analysis1123"
author: "YingtongZhou"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE}
setwd("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies")
```

Load Packages
```{r}
library(dplyr)
library(stringr)
library(readxl)
```


Load Data
```{r}
AleD <- read.table("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/AleD.txt", quote="\"", comment.char="")
names(AleD)[names(AleD) == "V1"] <- "ed"
AleD$ed <- paste(formatC(as.integer(sub("/.*", "", AleD$ed)), width=3, flag="0"),
                str_sub(AleD$ed,-2,-1), sep = "/")

FelD <- read.table("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/FelD.txt", quote="\"", comment.char="")
names(FelD)[names(FelD) == "V1"] <- "ed"
FelD$ed <- paste(formatC(as.integer(sub("/.*", "", FelD$ed)), width=3, flag="0"),
                str_sub(FelD$ed,-2,-1), sep = "/")

GE2016 <- read.csv("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/GE2016.csv", stringsAsFactors = FALSE)
GE2016$ed <- paste(formatC(GE2016$ED, width=3, flag="0"), formatC(GE2016$AD, width=2, flag="0"), sep="/")
GE2016$Tally <- as.numeric(GE2016$Tally)

ccd38 <- read.csv("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/17ccd38.csv", stringsAsFactors = FALSE)
ccd38$ed <- paste(formatC(ccd38$ED, width=3, flag="0"), formatC(ccd38$AD, width=2, flag="0"), sep="/")

ccd32 <- read.csv("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/17ccd32.csv", stringsAsFactors = FALSE)
ccd32$ed <- paste(formatC(ccd32$ED, width=3, flag="0"), formatC(ccd32$AD, width=2, flag="0"), sep="/")

Kings <- read_excel("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/KingsED_nov20.xlsx", skip = 4)
Kings <- na.omit(Kings)
Kings$ed <- paste(substr(Kings$`ELECTION DIST`, 9, 11), substr(Kings$`ELECTION DIST`, 7, 8), sep="/")

Qu <- read_excel("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/QueensED_nov20.xlsx", skip = 4)
Qu <- na.omit(Qu)
Qu$ed <- paste(substr(Qu$`ELECTION DIST`, 10, 12), substr(Qu$`ELECTION DIST`, 8, 9), sep="/")
```


2016 General Election Presidential - Alexa
```{r}
# Hillary Clinton
hc <- GE2016 %>% 
  filter(grepl('Hillary Clinton', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(hrc = sum(Tally))
pre16 <- left_join(AleD, hc, by = 'ed')

# Donald J. Trump
dt <- GE2016 %>% 
  filter(grepl('Donald J. Trump', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(dtc = sum(Tally))
pre16 <- left_join(pre16, dt, by = 'ed')

write.csv(pre16,'pre16Ale.csv')
```


2016 General Election Presidential - Felicia
```{r}
pre16f <- left_join(FelD, hc, by = 'ed')
pre16f <- left_join(pre16f, dt, by = 'ed')
write.csv(pre16f,'pre16Fel.csv')
```


2017 City Council - Alexa
```{r}
# Carlos Menchaca
cm <- ccd38 %>% 
  filter(grepl('Carlos Menchaca', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(cmc = sum(Tally))
ccdA <- left_join(AleD, cm, by = 'ed')

# Allan E. Romaguera
ar <- ccd38 %>% 
  filter(grepl('Allan E. Romaguera', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(arc = sum(Tally))
ccdA <- left_join(ccdA, ar, by = 'ed')

# Carmen V. Hulbert
ch <- ccd38 %>% 
  filter(grepl('Carmen V. Hulbert', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(chc = sum(Tally))
ccdA <- left_join(ccdA, ch, by = 'ed')

# Delvis Valdes
dv <- ccd38 %>% 
  filter(grepl('Delvis Valdes', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(dvc = sum(Tally))
ccdA <- left_join(ccdA, dv, by = 'ed')

write.csv(ccdA,'ccdA.csv')
```


2017 City Council - Felicia
```{r}
# Michael G. Scala 
ms <- ccd32 %>% 
  filter(grepl('Michael G. Scala ', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(msc = sum(Tally))
ccdF <- left_join(FelD, ms, by = 'ed')

# Eric A. Ulrich
eu <- ccd32 %>% 
  filter(grepl('Eric A. Ulrich', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(euc = sum(Tally))
ccdF <- left_join(ccdF, eu, by = 'ed')

write.csv(ccdF,'ccdF.csv')
```


2020 Registered Voters - Alexa D38
```{r}
TotalK <- Kings %>% 
  filter(STATUS == 'Total')

TotalQ <- Qu %>% 
  filter(STATUS == 'Total')

Total <- rbind(TotalK, TotalQ)

RV38 <- left_join(AleD, Total, by = 'ed')
write.csv(RV38, 'RV38.csv')
```


2020 Registered Voters - Felicia D32
```{r}
RV32 <- left_join(FelD, Total, by = 'ed')
write.csv(RV32, 'RV32.csv')
```


Add ccd7 ED/AD
```{r}
ccd7 <- read.csv("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/17ccd7.csv", stringsAsFactors = FALSE)
ccd7$ed <- paste(formatC(ccd7$ED, width=3, flag="0"), formatC(ccd7$AD, width=2, flag="0"), sep="/")

uccd7 <- ccd7 %>% 
  distinct(ed)
write.csv(uccd7, 'uccd7.csv')
```


Add Poll Site ccd7
```{r}
ps7 <- read_excel("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/ps7.XLSX")
ps7$ed <- paste(formatC(ps7$ED, width=3, flag="0"), formatC(ps7$AD, width=2, flag="0"), sep="/")
psccd7 <- left_join(uccd7, ps7, by = 'ed')
write.csv(psccd7, 'psccd7.csv')
```


2016 General Election Presidential - ccd7
```{r}
pre16d7 <- left_join(uccd7, hc, by = 'ed')
pre16d7 <- left_join(pre16d7, dt, by = 'ed')
write.csv(pre16d7,'pre16d7.csv')
```


2017 City Council ccd7
```{r}
# Mark D. Levine
ml <- ccd7 %>% 
  filter(grepl('Mark D. Levine', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(mlc = sum(Tally))
ccdS <- left_join(uccd7, ml, by = 'ed')

# Florindo J. Troncelliti
ft <- ccd7 %>% 
  filter(grepl('Florindo J. Troncelliti', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(ftc = sum(Tally))
ccdS <- left_join(ccdS, ft, by = 'ed')

write.csv(ccdS,'ccdS.csv')
```


2020 Registered Voters - Stacy D7
```{r}
ny <- read_excel("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/nyrv.xlsx")
ny <- na.omit(ny)
ny$ed <- paste(substr(ny$`ELECTION DIST`, 12, 14), substr(ny$`ELECTION DIST`, 10, 11), sep="/")
nyt <- ny %>% 
  filter(STATUS == 'Total')
RV7 <- left_join(uccd7, ny, by = 'ed')
write.csv(RV7, 'RV7.csv')
```


Added Neighborhoods - Remove Duplicate Rows
```{r}
psccd7 <- read.csv("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/psccd7.csv", stringsAsFactors = FALSE)
pst <- psccd7 %>% 
  select(Neighborhood, Site.Name, Site.Address) %>% 
  distinct()
write.csv(pst, 'pst.csv')
```


2020 Democratic Presidential - Eric Adam
```{r}
dp20 <- read.csv("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/DP2020.csv", stringsAsFactors = FALSE)
dp20$ed <- paste(formatC(dp20$X1, width=3, flag="0"), formatC(dp20$X65, width=2, flag="0"), sep="/")

alleds <- dp20 %>% 
  distinct(ed)

ex <- read_excel("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/ex.xlsx", col_names = TRUE)
ex7 <- psccd7 %>% 
  select(ed, Neighborhood, Site.Name)
eaed <- left_join(alleds, rbind(ex, ex7), by = "ed")
write.csv(eaed, 'AllEDs.csv')
```

