---
title: "EDAnalysis_0127"
author: "YingtongZhou"
date: "1/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies")
```


Load Packages
```{r}
library(dplyr)
library(stringr)
library(readxl)
```


Load 2017 ccd14 to get EDs
```{r}
ccd1417 <- read.csv("ccd1417.csv", header = TRUE, stringsAsFactors = FALSE)
ccd1417$ed <- paste(formatC(ccd1417$ED, width=3, flag="0"), formatC(ccd1417$AD, width=2, flag="0"), sep="/")
ccd1417_ed <- ccd1417 %>% 
  distinct(ed)
write.csv(ccd1417_ed, "ccd1417_ed.csv")
```


Load neighborhoods for ccd14
```{r}
ccd14n <- read.delim("ccd14nbh.txt", header = TRUE, stringsAsFactors = FALSE)
ccd14n$ed <- paste(formatC(as.integer(sub("/.*", "", ccd14n$ed)), width=3, flag="0"),
                 str_sub(ccd14n$ed, -2,-1), sep = "/")
ccd14nbh <- left_join(ccd1417_ed, ccd14n, by = "ed")
write.csv(ccd14nbh, "ccd14nbh.csv")
```


Load 2020 Presidential
```{r}
president2020 <- read.csv("2020President.csv", header = FALSE, stringsAsFactors = FALSE)
president2020$ed <- paste(formatC(president2020$V2, width=3, flag="0"), formatC(president2020$V1, width=2, flag="0"), sep="/")

# Absentee / Military
pre20ab <- president2020 %>% 
  select(-V1, -V2, -V3) %>% 
  filter(V4 == "Absentee / Military")
```


Join ccd14 & 2020President
```{r}
ab14 <- left_join(ccd1417_ed, pre20ab, by = "ed")
write.csv(ab14, "ab14.csv")
```


Biden2020 in ccd14
```{r}
president2020$V5 <- as.numeric(president2020$V5)
pre20b <- president2020 %>% 
  select(-V1, -V2, -V3) %>% 
  filter(grepl('Joseph R. Biden', V4)) %>% 
  group_by(ed) %>% 
  summarise(biden = sum(V5))

biden20 <- left_join(ccd1417_ed, pre20b, by = "ed")

pre20t <- president2020 %>% 
  select(-V1, -V2, -V3) %>% 
  filter(grepl('Donald J. Trump', V4)) %>% 
  group_by(ed) %>% 
  summarise(trump = sum(V5))

p20c14 <- left_join(biden20, pre20t, by = "ed")
```


Just add biden total to trump total for total votes; ignore this
```{r}
pre20sp <- president2020 %>% 
  select(-V1, -V2, -V3) %>% 
  spread(V4, V5)

pre20sp[is.na(pre20sp)] <- 0

pre20sp$ttl <- pre20sp$`Absentee / Military` + pre20sp$Federal + pre20sp$`Public Counter` + pre20sp$Scattered
prettl <- pre20sp %>% 
  select(ed, ttl)
p20ttl <- left_join(p20c14, prettl, by = "ed")
write.csv(p20ttl, "p20c14.csv")
```


2016 Presidential
```{r}
pre16 <- read.csv("GE2016.csv", stringsAsFactors = FALSE)
pre16$ed <- paste(formatC(pre16$ED, width=3, flag="0"), formatC(pre16$AD, width=2, flag="0"), sep="/")
pre16$Tally <- as.numeric(pre16$Tally)

pre16ab <- pre16 %>% 
  select(-AD, -ED) %>% 
  filter(Unit.Name == "Absentee / Military")

p16c14 <- left_join(ccd1417_ed, pre16ab, by = "ed")

hc <- pre16 %>% 
  filter(grepl('Hillary Clinton', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(hrc = sum(Tally))
p16c14 <- left_join(p16c14, hc, by = "ed")

dt <- pre16 %>% 
  filter(grepl('Donald J. Trump', Unit.Name)) %>% 
  group_by(ed) %>% 
  summarise(dtc = sum(Tally))
p16c14 <- left_join(p16c14, dt, by = "ed")

write.csv(p16c14, "p16c14.csv")
```


Congress district 13 2020 primary
```{r}
cd13p20 <- read.csv("cd13p20.csv", stringsAsFactors = FALSE, header = FALSE)
cd13p20$ed <- paste(formatC(cd13p20$V2, width=3, flag="0"), formatC(cd13p20$V1, width=2, flag="0"), sep="/")

# Ramon Rodriguez
result <- cd13p20 %>% 
  filter(grepl('Ramon Rodriguez', V3)) %>% 
  select(V4, ed) %>% 
  rename(RR = V4) %>% 
  right_join(ccd1417_ed)

# James Felton Keith II
result <- cd13p20 %>% 
  filter(grepl('James Felton Keith II', V3)) %>% 
  select(V4, ed) %>% 
  rename(JK = V4) %>% 
  right_join(result)

# Adriano Espaillat
result <- cd13p20 %>% 
  filter(grepl('Adriano Espaillat', V3)) %>% 
  select(V4, ed) %>% 
  rename(AE = V4) %>% 
  right_join(result)

write.csv(result, "result.csv")
```


Congress district 15 2020 primary
```{r}
cd15p20 <- read.csv("cd15p20.csv", stringsAsFactors = FALSE, header = FALSE)
cd15p20$ed <- paste(formatC(cd15p20$V2, width=3, flag="0"), formatC(cd15p20$V1, width=2, flag="0"), sep="/")

# Ritchie Torres
result2 <- cd15p20 %>% 
  filter(grepl('Ritchie Torres', V3)) %>% 
  select(V4, ed) %>% 
  rename(RT = V4) %>% 
  right_join(ccd1417_ed)

# Michael Blake
result2 <- cd15p20 %>% 
  filter(grepl('Michael A. Blake', V3)) %>% 
  select(V4, ed) %>% 
  rename(MB = V4) %>% 
  right_join(result2, by = "ed")

# Ruben Diaz
result2 <- cd15p20 %>% 
  filter(grepl('Ruben Diaz', V3)) %>% 
  select(V4, ed) %>% 
  rename(RD = V4) %>% 
  right_join(result2, by = "ed")

# Samelys Lopez
result2 <- cd15p20 %>% 
  filter(grepl('Samelys Lopez', V3)) %>% 
  select(V4, ed) %>% 
  rename(SL = V4) %>% 
  right_join(result2, by = "ed")

# Ydanis Rodriguez
result2 <- cd15p20 %>% 
  filter(grepl('Ydanis Rodriguez', V3)) %>% 
  select(V4, ed) %>% 
  rename(YR = V4) %>% 
  right_join(result2, by = "ed")

# Melissa Mark-Viverito
result2 <- cd15p20 %>% 
  filter(grepl('Melissa Mark-Viverito', V3)) %>% 
  select(V4, ed) %>% 
  rename(MM = V4) %>% 
  right_join(result2, by = "ed")

# Tomas Ramos
result2 <- cd15p20 %>% 
  filter(grepl('Tomas Ramos', V3)) %>% 
  select(V4, ed) %>% 
  rename(TR = V4) %>% 
  right_join(result2, by = "ed")

# Chivona R. Newsome
result2 <- cd15p20 %>% 
  filter(grepl('Chivona R. Newsome', V3)) %>% 
  select(V4, ed) %>% 
  rename(CN = V4) %>% 
  right_join(result2, by = "ed")

write.csv(result2, "result2.csv")
```


Congress district 13 2016 primary
```{r}
cd13p16 <- read.csv("cd13p16.csv", stringsAsFactors = FALSE, header = TRUE)
cd13p16$ed <- paste(formatC(cd13p16$ED, width=3, flag="0"), formatC(cd13p16$AD, width=2, flag="0"), sep="/")

# Adriano Espaillat
result3 <- cd13p16 %>% 
  filter(grepl('Adriano Espaillat', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(AE = Tally) %>% 
  right_join(ccd1417_ed)

# Keith L. T. Wright
result3 <- cd13p16 %>% 
  filter(grepl('Keith L. T. Wright', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(KW = Tally) %>% 
  right_join(result3)

# Clyde E. Williams
result3 <- cd13p16 %>% 
  filter(grepl('Clyde E. Williams', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(CW = Tally) %>% 
  right_join(result3)

# Adam Clayton Powell
result3 <- cd13p16 %>% 
  filter(grepl('Adam Clayton Powell', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(AP = Tally) %>% 
  right_join(result3)

# Guillermo Linares
result3 <- cd13p16 %>% 
  filter(grepl('Guillermo Linares', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(GL = Tally) %>% 
  right_join(result3)

# Suzan D. Johnson-Cook
result3 <- cd13p16 %>% 
  filter(grepl('Suzan D. Johnson-Cook', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(SC = Tally) %>% 
  right_join(result3)

write.csv(result3, "result3.csv")
```


Assembly district 78 2016 primary
```{r}
ad78p16 <- read.csv("ad78p16.csv", stringsAsFactors = FALSE, header = TRUE)
ad78p16$ed <- paste(formatC(ad78p16$ED, width=3, flag="0"), formatC(ad78p16$AD, width=2, flag="0"), sep="/")

# Jose Rivera
result4 <- ad78p16 %>% 
  filter(grepl('Jose Rivera', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(JR = Tally) %>% 
  right_join(ccd1417_ed, by = "ed")

# Ischia J. Bravo
result4 <- ad78p16 %>% 
  filter(grepl('Ischia J. Bravo', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(IB = Tally) %>% 
  right_join(result4, by = "ed")

write.csv(result4, "result4.csv")
```


Assembly district 86 2016 primary
```{r}
ad86p16 <- read.csv("ad86p16.csv", stringsAsFactors = FALSE, header = TRUE)
ad86p16$ed <- paste(formatC(ad86p16$ED, width=3, flag="0"), formatC(ad86p16$AD, width=2, flag="0"), sep="/")

# Victor M. Pichardo
result5 <- ad86p16 %>% 
  filter(grepl('Victor M. Pichardo', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(VP = Tally) %>% 
  right_join(ccd1417_ed, by = "ed")

# Hector R. Ramirez
result5 <- ad86p16 %>% 
  filter(grepl('Hector R. Ramirez', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(HR = Tally) %>% 
  right_join(result5, by = "ed")

write.csv(result5, "result5.csv")
```


Assembly district 86 2014 primary
```{r}
ad86p14 <- read.csv("ad86p14.csv", stringsAsFactors = FALSE, header = TRUE)
ad86p14$ed <- paste(formatC(ad86p14$ED, width=3, flag="0"), formatC(ad86p14$AD, width=2, flag="0"), sep="/")

# Victor M. Pichardo
result6 <- ad86p14 %>% 
  filter(grepl('Victor M. Pichardo', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(VP = Tally) %>% 
  right_join(ccd1417_ed, by = "ed")

# Hector R. Ramirez
result6 <- ad86p14 %>% 
  filter(grepl('Hector R. Ramirez', Unit.Name)) %>% 
  select(Tally, ed) %>% 
  rename(HR = Tally) %>% 
  right_join(result6, by = "ed")

write.csv(result6, "result6.csv")
```


Assembly district 81 2020 primary
```{r}
ad81p20 <- read.csv("ad81p20.csv", stringsAsFactors = FALSE, header = FALSE)
ad81p20$ed <- paste(formatC(ad81p20$V2, width=3, flag="0"), formatC(ad81p20$V1, width=2, flag="0"), sep="/")

# George Diaz
result7 <- ad81p20 %>% 
  filter(grepl('George Diaz', V3)) %>% 
  select(V4, ed) %>% 
  rename(GD = V4) %>% 
  right_join(ccd1417_ed, by = "ed")

# Jeffrey Dinowitz
result7 <- ad81p20 %>% 
  filter(grepl('Jeffrey Dinowitz', V3)) %>% 
  select(V4, ed) %>% 
  rename(JD = V4) %>% 
  right_join(result7, by = "ed")

write.csv(result7, "result7.csv")
```

