---
title: "ED_Analysis1216"
author: "YingtongZhou"
date: "12/16/2020"
output: html_document
---

```{r setup, include=FALSE}
setwd("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies")
```

Load Packages
```{r}
library(dplyr)
library(stringr)
library(readxl)
library(rgdal)
library(leaflet)
library(RColorBrewer)
library(tidyverse)
library(sf)
```


Load NYC EDs shapefile
```{r}
nyed <- readOGR("~/Desktop/GeoSpatial/nyedwi_20d/nyedwi.shp")
nyed@data$ElectDist <- as.numeric(as.character(nyed@data$ElectDist))
nyed <- spTransform(nyed, CRS("+proj=longlat +datum=WGS84 +no_defs"))
plotnyed <- plot(nyed)
```


Load 2020 presidential results and join nyed
```{r}
pre20 <- read.csv("pre20ED.csv", header = TRUE)
nyed@data <- left_join(nyed@data, pre20, by = c("ElectDist" = "ED"))
```


Set color bins for jbc & dtc
```{r}
bins <- c(0, 50, 100, 200, 300, 400, 500, 800, Inf)
palb <- colorBin("Blues", domain = nyed$jbc, bins = bins)
palr <- colorBin("Reds", domain = nyed$dtc, bins = bins)
```


Add labels
```{r}
contentb <- paste("ElectDistrict:", nyed$ElectDist,
                 "Biden:", nyed$jbc,
                 "Trump:", nyed$dtc)
```


Load Eds for ccd 31 and Subset ccd31 from nyed
```{r}
ccd31 <- read.delim("~/Desktop/QMSS - CU/JobHunting/ElevationStrategies/ccd31.txt", stringsAsFactors = FALSE)
ccd31$ed <- paste(str_sub(ccd31$ed, -2,-1), formatC(as.integer(sub("/.*", "", ccd31$ed)), width=3, flag="0"), sep = '')

sp31 <- nyed[nyed$ElectDist %in% ccd31$ed, ]
```


Get outline for for ccd31
```{r}
nyed2 <- sf::st_as_sf(nyed)

poly31 <- nyed2 %>%
  filter(nyed2$ElectDist %in% ccd31$ed) %>%
  summarise(ElectDist = "ccd31")

# (mp31 <- leaflet()  %>% 
#       setView(lng = -73.934314, lat = 40.687000,zoom = 10) %>% 
#       addTiles() %>% 
#       addPolygons(data = poly31,
#                   weight = 2,
#                   color = "brown",
#                   group = "ccd31 Outline"))
```


Load and join NYC Census Tracts & Queens Demographic Info
```{r}
quct <- readOGR("~/Desktop/GeoSpatial/NYC_CensusTract/nyu_2451_34505.shp")
quct <- spTransform(quct, CRS("+proj=longlat +datum=WGS84 +no_defs"))
plotquct <- plot(quct)
quct@data$namelsad <- as.numeric(substring(sub("\\,.*", "", quct@data$namelsad), 14))

qdem <- read.csv("~/Desktop/GeoSpatial/ACS_Queens/qc2.csv", skip = 1)
qdem <- qdem %>% 
   select(-X, -X.1)

quct@data <- left_join(quct@data, qdem, by = c("namelsad" = "CT"))
quct$White. <- as.numeric(as.character(quct$White.))
quct$Black. <- as.numeric(as.character(quct$Black.))
quct$Asian. <- as.numeric(as.character(quct$Asian.))
quct$Hispanic. <- as.numeric(as.character(quct$Hispanic.))
```


Set color bins for demographics
```{r}
bins2 <- c(0, 12.5, 25, 37.5, 50, 62.5, 75, 87.5, 100)
palw <- colorBin("Purples", domain = quct$White., bins = bins2)
pala <- colorBin("Greens", domain = quct$Black., bins = bins2)
pals <- colorBin("Oranges", domain = quct$Asian., bins = bins2)
palh <- colorBin("Greys", domain = quct$Hispanic., bins = bins2)
```


Add demographic info labels
```{r}
contentd <- paste("Census Tract#:", quct$namelsad,
                  "White%:", quct$White.,
                  "Black%:", quct$Black.,
                  "Asian%:", quct$Asian.,
                  "Hispanic%:", round(quct$Hispanic., 2))
```


Census tract map - White%
```{r}
# (mpct <- leaflet()  %>%
#     setView(lng = -73.934314, lat = 40.687000,zoom = 10) %>%
#     addTiles() %>%
#     addPolygons(data = quct, 
#                 fillColor = ~palw(White.),
#                 weight = 1,
#                 color = "yellow",
#                 label = contentd,
#                 fillOpacity = 0.9))
```


Load NYC School District
```{r}
sd <- readOGR("~/Desktop/GeoSpatial/nysd_20d/nysd.shp")
sd <- spTransform(sd, CRS("+proj=longlat +datum=WGS84 +no_defs"))
plotsd <- plot(sd)
```


Map NY School District
```{r}
(msd <- leaflet()  %>%
      setView(lng = -73.934314, lat = 40.687000,zoom = 10) %>%
      addTiles() %>%
      addPolygons(data = sd,
                  weight = 2,
                  color = "black",
                  label = paste("School District", sd$SchoolDist),
                  group = "School District"))
```





Show NYC all EDs in leaflet
```{r}
(plot2 <- leaflet()  %>% 
    setView(lng = -73.934314, lat = 40.687000,zoom = 10) %>% 
    addTiles(group = "OSM (default)") %>%
    addProviderTiles(providers$Stamen.Toner, group = "Toner") %>%
    addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
    addPolygons(data = nyed,
                fillColor = ~palb(jbc),
                weight = 1,
                fillOpacity = 0.9,
                label = contentb,
                group = "Biden NYC") %>%
    addPolygons(data = sp31, 
                fillColor = ~palb(jbc),
                weight = 1,
                fillOpacity = 0.9，
                label = contentb,
                group = "Biden ccd31") %>%
    addPolygons(data = nyed, 
                fillColor = ~palr(dtc),
                weight = 1,
                color = "red",
                fillOpacity = 0.9，
                label = contentb,
                group = "Trump NYC") %>% 
    addPolygons(data = sp31, 
                fillColor = ~palr(dtc),
                weight = 1,
                color = "red",
                fillOpacity = 0.9，
                label = contentb,
                group = "Trump ccd31") %>% 
    addPolygons(data = poly31,
                weight = 2,
                color = "brown",
                group = "ccd31 Outline") %>% 
    addPolygons(data = quct, 
                fillColor = ~palw(White.),
                weight = 1,
                color = "yellow",
                label = contentd,
                fillOpacity = 0.9,
                group = "White%") %>% 
    addPolygons(data = quct, 
                fillColor = ~pala(Black.),
                weight = 1,
                color = "yellow",
                label = contentd,
                fillOpacity = 0.9,
                group = "Black%") %>% 
    addPolygons(data = quct, 
                fillColor = ~pals(Asian.),
                weight = 1,
                color = "yellow",
                label = contentd,
                fillOpacity = 0.9,
                group = "Asian%") %>% 
    addPolygons(data = quct, 
                fillColor = ~palh(Hispanic.),
                weight = 1,
                color = "yellow",
                label = contentd,
                fillOpacity = 0.9,
                group = "Hispanic%") %>% 
    addPolygons(data = sd,
                weight = 2,
                color = "black",
                label = paste("School District", sd$SchoolDist),
                group = "School District") %>% 
    addLayersControl(
       baseGroups = c("OSM (default)", "Toner", "Toner Lite"),
       overlayGroups = c("Biden NYC", "Biden ccd31", "Trump NYC", "Trump ccd31", "ccd31 Outline",
                         "White%", "Black%", "Asian%", "Hispanic%", "School District"),
       options = layersControlOptions(collapsed = FALSE)) %>% 
   hideGroup("Biden ccd31", "Trump NYC", "Trump ccd31", "ccd31 Outline",
             "White%", "Black%", "Asian%", "Hispanic%", "School District"))
```



